%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.11 (19/6/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{red} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

\usepackage{enumitem} % For itemize, and item separation

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Madison} % Your first name
\familyname{Sheridan} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\mobile{(916) 790-7806}
\email{madison.sheridan94@gmail.com}
\homepage{helblindi.github.io}{helblindi.github.io}
%\homepage{https://www.linkedin.com/pub/daniele-perrotta/64/5b9/794} {staff.org.edu/$\sim$jsmith} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\extrainfo{additional information}
% \photo[90pt][0.7pt]{pictures/photo1.png} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------
\newcommand{\Csharp}{%
  {\settoheight{\dimen0}{C}C\kern-.05em \resizebox{!}{\dimen0}{\raisebox{\depth}{\textbf{\#}}}}}
\begin{document}

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	RESEARCH INTERESTS
%----------------------------------------------------------------------------------------
\section{Research Interests}
\cventry{}{\normalfont Numerical methods for PDEs, Hyperbolic systems of conservation laws, Computational fluid dynamics, Compressible Euler equations, Lagrangian hydrodynamics}{}{}{}{}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}
\cventry{2019--2025}{PhD, Mathematics}{Texas A\&M University}{College Station, TX}{}{\textbf{Thesis:} A Robust Lagrangian Framework for Compressible Flow \& Hyperelasticity \\%GPA
}{%\textbf{Thesis Title:} Unsupervised Interaction Detection in Videos Sequences\\

%{Status:} In the writing phase}  % Arguments not required can be left empty
}

\cventry{2015--2019}{Bachelor of Science, Mathematics (Computer Science minor)}{Brigham Young University -- Idaho}{Rexburg, ID}{}{%GPA: 
} 

%\section{Masters Thesis}

%\cvitem{Title}{\emph{Technologies and characterization of ferroelectric polymers for biomedical sensors}}
%\cvitem{Supervisors}{Professor Antonino Fiorillo}
%\cvitem{Description}{This thesis is based on the implementation of a temperature sensor.}

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}
 
\cventry{2019--2025}{Graduate Teaching/Research Assistant}{Texas A\&M University}{}{College Station, TX}{
\textbf{Advisor: Jean-Luc Guermond}
\normalfont
\begin{itemize}
    % \itemsep -3pt {} 
    \item Developed a finite element method for the equations of Lagrangian hydrodynamics that achieves high-order accuracy while preserving essential physical invariants, ensuring robustness in challenging flow regimes.
    % \item Implemented novel techniques in C++ within MFEM, validated through convergence studies, benchmark problems, and HPC runs on the Whistler cluster.
    \item Collaborated across mathematics, physics, and engineering teams; presented findings at SIAM CSE, USNCCM, and other national conferences.
    \item Served as Instructor of Record for Math 140, independently leading classroom instruction, developing assignments and exams, and evaluating student performance.
 \end{itemize}
% Entry to show diversity of experience, can remove if applying to strictly math positions
% \textbf{Co-Advisor: Jim Morel}
% \normalfont
% \begin{itemize}
%     \item Variable Eddington Factor (VEF) method for the 1-D grey radiative transfer equations
% \end{itemize}
} 
% \cventry{2024}{Instructor of Record}{Texas A\&M University}{College Station, TX}{}{
% \begin{itemize}
%     \item Mathematics for Business and Social Sciences
% \end{itemize}
% }
\cventry{2022--2023}{Graduate Student Intern}{Lawrence Livermore National Laboratory}{Livermore, CA}{}{ 
\textbf{Mentor: Vladimir Tomov} 
\normalfont
\begin{itemize}
    \item Augmented high-order Lagrangian hydrodynamics codes in C++/MFEM with an invariant-domain preserving Lagrangian finite element method, ensuring physics-consistent robustness validated with benchmark tests.
    \item Modified an MFEM discontinuous Galerkin advection solver for use with continuous finite element discretizations, extending code capabilities and supporting broader benchmarking.
\end{itemize}
} 

\cventry{2019--2022}{Graduate Student Intern}{Nevada National Security Site}{North Las Vegas, NV}{}{ 
\textbf{Mentors: Cleat Zeiler, Marylesa Howard, Daniel Champion, Jesse Adams} 
\normalfont
\begin{itemize}
    % \itemsep -3pt {} 
     \item Developed and trained deep learning models in Python/TensorFlow to reconstruct clipped seismic waveforms, improving signal fidelity and enabling more accurate seismic event detection.
    \item Designed a Python-based multilateration algorithm using geophone array data to geolocate seismic signal sources with improved accuracy, supporting rapid deployment for field missions.
 \end{itemize}
} 

\section{Publications}
\cvitem{2025}{Guermond, J.-L., Popov, B., Saavedra, L., Sheridan, M., \textit{"Invariant-domain-preserving and locally mass conservative approximation of the Lagrangian hydrodynamics equations,"} Computer Methods in Applied Mechanics and Engineering}
% \cvitem{2021}{Zeiler, C., McLin, K., Champion, D., Scalise, Michelle., Sheridan, M., White, R., Jensen, R., Smith, K., Plank, G., \textit{“The Monte Cristo Range Mw 6.5 Nodal Geophone Rapid Deployment”}}

\section{Talks}
% 2025
\cvitem{2025}{\textit{A Robust Lagrangian Framework for Compressible Flow \& Hyperelasticity}, Dissertation Defense, Texas A\&M University, College Station, TX, USA. October 2025.}
\cvitem{2025}{\textit{A Robust Lagrangian Framework for Compressible Flow \& Hyperelasticity}, Mathematics Graduate Student Organization Seminar, Texas A\&M University, College Station, TX, USA. September 2025.}
\cvitem{2025}{\textit{Invariant-Domain-Preserving Approximation of the Lagrangian Hydrodynamics Equations}, LANL Center for Nonlinear Studies Seminar Series, Los Alamos, NM, USA. September 2025.}
% 2024
\cvitem{2024}{\textit{Invariant-Domain-Preserving and Exactly Conservative Approximation of the Lagrangian Hydrodynamics Equations}, 7th Annual Meeting of the SIAM Texas-Louisiana Section, Baylor University, Waco, TX, USA. October 2024.}
\cvitem{2024}{\textit{Invariant-Domain-Preserving and Exactly Conservative Approximation of the Lagrangian Hydrodynamics Equations}, Second annual RTG NASC Annual Workshop, Rice University, Houston, TX, USA. October 2024.}
\cvitem{2023}{\textit{Invariant-Domain-Preserving and Exactly Conservative Approximation of the Lagrangian Hydrodynamics Equations}, 6th Annual Meeting of the SIAM Texas-Louisiana Section, University of Louisiana at Lafayette, Lafayette, LA, USA. November 2023.}

\cvitem{2023}{\textit{A Brief Introduction to Finite Element Methods}, Applied Mathematics Undergraduate SEminar (AMUSE), Texas A\&M University, College Station, TX, USA. October 2023.}

\cvitem{2023}{\textit{Invariant-Domain-Preserving and Exactly Conservative Approximation of the Lagrangian Hydrodynamics Equations}, Intern Final Presentations, Livermore, CA, USA. August 2023.}

\cvitem{2023}{\textit{Invariant-Domain-Preserving and Exactly Conservative Approximation of the Lagrangian Hydrodynamics Equations}, 17th U. S. National Congress on Computational Mechanics, Albuquerque, NM, USA. July 2023.}

\cvitem{2023}{\textit{Invariant-Domain-Preserving and Exactly Conservative Approximation of the Lagrangian Hydrodynamics Equations}, Finite Element Rodeo, Texas A\&M University, College Station, TX, USA. March 2023.}

\cvitem{2023}{\textit{Invariant-Domain-Preserving and Exactly Conservative Approximation of the Lagrangian Hydrodynamics Equations}, SIAM Conference on Computational Science and Engineering (CSE23), Amsterdam, The Netherlands. February 2023.}

\cvitem{2022}{\textit{Invariant Domains and a First-Order Continuous Finite Element Approximation}, Intern Final Presentations, Livermore, CA, USA. August 2022.}

\cvitem{2021}{\textit{Invariant Domain Preserving IMEX Methods}, SIAM TX-LA Meeting, University of Texas Rio Grande Valley, South Padre Island, TX, USA. November 2021.}

\section{Posters}
\cvitem{2025}{\textit{Invariant-Domain-Preserving and Exactly Conservative Approximation of the Lagrangian Hydrodynamics Equations}, Hypersonics Workshop, College Station, TX, USA. August 2025.}
\cvitem{2023}{\textit{Invariant-Domain-Preserving and Exactly Conservative Approximation of the Lagrangian Hydrodynamics Equations}, Intern Poster Presentations, Livermore, CA, USA. August 2023.}
\cvitem{2023}{\textit{Invariant-Domain-Preserving and Exactly Conservative Approximation of the Lagrangian Hydrodynamics Equations}, 7th KUMUNU-ISU Conference in PDE, Dynamical Systems and Applications, Iowa State University, Aimes, IA, USA. April 2023.}
\cvitem{2019}{\textit{Seismic Clipped Waveform Reconstruction and Noise Attenuation Using Deep Learning}, 
American Geophysical Union Fall Meeting, San Francisco, CA, USA. December 2019.}

\section{Leadership}
\cventry{2023}{Organizer}{Mini-symposium on "Invariant-Domain Preserving Hydrodynamics: From Euler to Navier-Stokes"}{17th U. S. National Congress on Computational Mechanics, July 2023}{}{}

\cventry{2022}{Organizer}{Mini-symposium on "High Order Methods for Computational Hydrodynamics"}{5th Annual Meeting of the SIAM Texas-Louisiana Section (TXLA22), November 2022}{}{}

\cventry{2019--2024}{President, Vice President, Treasurer}{Society for Industrial and Applied Math Graduate Student Chapter,
Texas A\&M University}{}{}{}

\section{Software development}
\cventry{2021--Present}{MFEM}{LLNL}{Scalable C++ library for finite element methods}{}{}
% \cventry{2021--Present}{LAGLOS}{Texas A\&M University}{C++ library for Lagrangian hydrodynamics using discontinuous finite elements}{}{}
\cventry{2020--Present}{Ryujin}{Texas A\&M University}{high-performance high-order collocation-type finite-element solver for conservation equations}{}{}

\section{Outreach/Mentorship}
\cvitem{2024}{\textbf{Mentor}, Advised an undergraduate research project on nonlinear elasticity for the Modeling and Simulation with PDEs summer school, Texas A\&M University}
\cvitem{2023}{\textbf{Volunteer}, Mathematics and Statistics Fair, Texas A\&M University}
\cvitem{2022}{\textbf{Mentor}, Advised an undergraduate research project studying chemotaxis for the Directed Reading Program, Texas A\&M University}

\cvitem{2021--2022}{\textbf{GED Prep Instructor}, B/CS Community Education Center, Bryan, TX}

\cvitem{2019}{\textbf{Proctor}, High School Math Contest, Texas A\&M University}

% \cvitem{2013 -- 2015}{\textbf{Missionary}, Church of Jesus Christ of Latter Day Saints, Porto Alegre, Rio Grande do Sul, Brazil \& Twin Falls, ID, USA.}

\cvitem{2011}{\textbf{Eagle Scout}, El Dorado Hills, CA.}

\section{Membership}
\cvitem{}{American Mathematical Society (AMS)}
\cvitem{}{Society for Industrial and Applied Mathematics (SIAM)}

% \section{Skills and Activities}
% \cvitem{Programming Language}{{MATLAB,C++, Java, \Csharp, VB.net, MySQL}}
% \cvitem{Web }{{ASP, HTML, XML, WebServices (SOAP)}}
% \cvitem{IDE }{{VisualStudio.net, Qt Creator (Basic)}}
% \cvitem{Environment }{{OpenCV, Latex}, Microsoft Office}
% \cvitem{Operating System }{Windows, Linux}


%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------
\section{Computer Languages}
\cvitem{}{Proficient in: C++, Python, LaTeX, Git, Lisp, Mathematica}
\cvitem{}{Knowledgeable in: Java, JavaScript, Fortran2003, Matlab}

\section{Languages}
\cvitem{English}{{Native Language}}
\cvitem{Portuguese}{Intermediate Listener, Intermediate Speaker, Advanced Reader, Novice Writer}

%\cvitemwithcomment{Arabic}{Native Speaker}{}
%\cvitemwithcomment{English}{\textsc{English (TOEFL)(Bachelor, Master, and PhD in English, Master and PhD dissertations
%written in English, numerous publications and presentations in English, teaching in the
%international Master Program and Bachelor Program in English)}
%}{}
%\cvitemwithcomment{German}{Professional working proficiency}{}


%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------
\iffalse
\section{Competenze Informatiche}

\cvitem{Linguaggi program}{\textsc{Java, Android, MySQL, MATLAB}}
\cvitem{Web }{\textsc{CMS, HTML, XML, XSL, XSLT, XPATH, JAVASCRIPT}, Subversion, Apache, Tomcat, WebServices (SOAP)}
\cvitem{IDE }{\textsc{Eclipse, NetBeans, Android Studio, VisualStudio}}


\cvitem{Tecnologie }{\textsc{MVC}, \textsc{J2EE}, \textsc{Hibernate}, Spring Framework, JSF, Primefaces, Liferay}
\cvitem{Database }{PostgreSQL, Oracle, DB2}
\cvitem{Sistemi Operativi }{Windows, Unix, Macintosh}

\section{Competenze Tecniche}

\cvitem{Software }{\textsc{MATLAB, SPM, Cadence PSPICE, LabView}}

\section{Progetti IT}

\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\cvlistitem{Sviluppo di un Sistema per la gestione di Ticketing}
\cvlistitem{Manutenzione  Evolutiva del Portale  ARPACAL (Agenzia  Regionale per  la Protezione dell'Ambiente della Calabria)}
\cvlistitem{Sviluppo di un sistema per la gestione delle Tasse di Concessione Regionale (TCR)}
\cvlistitem{Sviluppo di un Sistema per la gestione dei Verbali}
\cvlistitem{Manutenzione Evolutiva del Portale dei Tributi della Regione Calabria}
\cvlistitem{Sviluppo di un Sistema per la gestione delle Minute e delle Pratiche di Equitalia    attraverso l'interazione tramite Web Service}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

%\section{Communication Skills}

%\cvitem{2010}{Oral Presentation at the California Business Conference}
%\cvitem{2009}{Poster at the Annual Business Conference in Oregon}

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Lingue}

\cvitemwithcomment{Italiano}{Madrelingua}{}
\cvitemwithcomment{Inglese}{Livello Intermedio}{}
%\cvitemwithcomment{Dutch}{Basic}{Basic words and phrases only}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Interessi}

\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\cvlistdoubleitem{Piano}{}
\cvlistitem{Atletica}
\fi
%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage

%\recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

%\makelettertitle % Print letter title

%\lipsum[1-3] % Dummy text

%\makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------

\end{document}



